### 2013-12-16 thesis/src/chapters/chapter-7-evaluation.tex
Add deployment time test description

\section{Service deployment}
\subsection{Description and preconditions}
The aim of this test case is to test the primary use case of the proposed solution -- deployment of a service with the emphasis of client's \textbf{cost}.
Service specification (\ref{lst:service-spec-test-cost}) forms an input to the application. Its elements are different software stacks that are parts of the whole service. Each cloud provider has its own price for a given software stack which is shown in table \ref{tbl:test-service-deployment-cost}.
This test should show that the platform chooses the best mapping between the stacks and cloud providers so that the client's pays the \textbf{lowest} possible price.

@@

>>>>

\section{Cost of service deployment}
\subsection{Description and preconditions}
The aim of this test case is to test the primary use case of the proposed solution -- deployment of a service with the emphasis of client's \textbf{cost}.
Service specification (\ref{lst:service-spec-test-cost}) forms an input to the application. Its elements are different software stacks that are parts of the whole service. Each cloud provider has its own price for a given software stack which is shown in table \ref{tbl:test-service-deployment-cost}.
This test should show that the platform chooses the best mapping between the stacks and cloud providers so that the client's pays the \textbf{lowest} possible price.

@@

\section{Deployment time -- solution comparison}
\subsection{Motivation}
In this test we want to compare our solution to one of those available at the market which use \emph{OpenNebula} as an underlying tool for managing resources of a data center in terms of \textbf{deployment time}, one of the most important factors of products whose main purpose is to scale applications.
\emph{Carina} \cite{Carina} can be considered a perfect match of a solution for such a comparison and tests are ran against it.
\subsection{Description and preconditions}
\subsubsection{Service description}
The service comprises a simple java enterprise application, deployed in a master-slave configuration with one VM set as a load balancer and other nodes that serve as workers, which uses Tomcat as a web container.

TODO dodać konfigurację każdej z maszyn wirtualnych
\subsubsection{Hardware configuration}
All virtual machines were deployed on one node which had 3G RAM, AMD Athlon\texttrademark 64 X2 Dual Core Processor with each core of 2000 MHz frequency and a hard drive with a capacity of 160 GB.
\subsection{Results}

\section{Deployment time -- hypervisor comparison}
